An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With Application to Australian Maps

### 2019-03-27 algorithmRjournal/algorithmRjournal.tex
R journal template draft

---
title: An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With Application to Australian Maps
author:
  - name: Stephanie Kobakian
    affiliation: Queensland Univeristy of Technology
    email:  stephanie.kobakian@monash.edu
  - name: Dianne Cook
    affiliation: Monash University
    email:  dicook@monash.edu
abstract: >
  This algorithm creates a hexagon to represent each of the spatial polygons provided. It allocates these hexagon in a manner that preserves the spatial relationship of the areas. It showcases spatial distributions, by emphasising the small geograhical regions that are often diffcult to locate on large geographic maps.
output:
  rticles::rjournal_article:
    includes:
      in_header: preamble.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
  cache = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.height = 3, fig.width = 3)
```

## Introduction

@@

## Motivation

@@

# Algorithm

Our solution operates on a set of polygons.
There are parameters used in the process that may be provided, or will be automatically derived.
All necessary functions are exported, with a main function `create_hexmap` used to step through these automatically.

## Parameters

The `create_hexmap` function requires several parameters, if they are not provided, the information will be derived from the polygon set used.

**The following must be provided to `create_hexmap`:**
```{r table_necessary}
knitr::kable(tibble::tibble(parameter = c('shp', 
  'shp_path',
  'sf_id',
  'capital_cities'),
  description = c('an Rdata object containing the polygon information', 'character string location of the shape file that contains the polygon information', 'name of a unique column that distinguishes areas',
    'a data frame of reference locations used to allocate hexagons'
    )), format = "latex")

```

```{r libraries}
library(tidyverse)
# To install sugarbag:
# devtools::install_github("srkobakian/sugarbag")
library(sugarbag)
```

The polygon set of Local Government Areas in Tasmania in 2016 is stored in the sugarbag package data as `tas_lga`. 
A single column of the data set must be used as a unique identifier of areas. In this case, the unique LGA codes associated with each LGA have been used, their names could have also been used.

```{r id}
sf_id <- "LGA_CODE16"
```

@@

```{r data}
data(capital_cities)
```

**The following parameters will be determined within `create_hexmap` if not provided. They are created throughout the following example:**

```{r}
knitr::kable(tibble(parameter = c('buffer_dist', 'hex_size',  'hex_filter', 'width'),
  description = c('a float value for distance in degrees to extend beyond the - geometry provided',
    'a float value in degrees for the diameter of the hexagons', 'amount of hexagons around centroid to consider for allocation',
    'the angle used to filter the grid points around a centroid')), format = "latex")
```

When utilising individual `sugarbag` functions, we recommend the following approach:

## Polygon Information

Begin with a set of polygons. The set should be provided as an `sf` object, this is a data frame containing a `geometry` column. The `read_shape` function can assist in creating this object. We will use the Loca Goverment Areas of Tasmania, sourced from the Australian Bureau of Statistics.

```{r}
# Create a suitable data set for plotting
fort_lga <- fortify_sfc(tas_lga)

# Include area variable
area_var <- fort_lga %>% 
  distinct(LGA_CODE16, .keep_all = TRUE) %>% 
  select(LGA_CODE16, AREASQKM16)
```

```{r centroids}
## Use the create_centroids function to find polygon centroids:
centroids <- create_centroids(shp_sf = tas_lga, sf_id = sf_id) %>%
  left_join(., select(area_var, LGA_CODE16, AREASQKM16), by = "LGA_CODE16")
```

```{r, fig.cap="lga Local Government Areas and derived centroids."}
end_cents <- ggplot() + 
  geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids) + theme_void() + coord_equal()
end_cents

#ggplot() + geom_histogram(aes(x = log(AREASQKM16), fill = log(AREASQKM16)), data= centroids, bins = 20) 
```

## Hexagon grid

Each new hexagon will need to tesselate, a grid is created to ensure a close point is found, that will allow all areas to tesselate, this is inspired by tilegrams. The grid of possible hexagon centroids can be made using the `create_grid` function. The grid creation takes several steps. It requires the centroids, the hexagon size and the buffer distance.

```{r bbox}
## create the bounding box from the set of polygon centroids:
bbox <- tibble::tibble(min = c(min(centroids$longitude, na.rm = TRUE), min(centroids$latitude, na.rm = TRUE)),
        max = c(max(centroids$longitude, na.rm = TRUE), max(centroids$latitude, na.rm = TRUE)))

hex_size <- 0.2

# default size calculation:
#(bbox$max[1] - bbox$min[1])/(bbox$max[2] - bbox$min[2]) / 5

buffer_dist <- max((bbox$max[1] - bbox$min[1]), (bbox$max[2] - bbox$min[2]))*0.3
```

### Step 1: Expand the grid

@@

```{r grid}
grid <- tibble::as_tibble(
  expand.grid(
    hex_long = seq(bbox$min[1] - buffer_dist, # minimum
      bbox$max[1] + buffer_dist, # maximum
      hex_size), # distance between hexagons
    hex_lat = seq(bbox$min[2] - buffer_dist, # minimum
      bbox$max[2] + buffer_dist, # maximum
      hex_size))) # distance between hexagons
```

```{r plot_grid}
ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
```

@@

```{r shift}
# Find every second latitude
shift_lat <- grid %>% dplyr::select(hex_lat) %>%
    dplyr::distinct() %>%
    dplyr::filter(dplyr::row_number() %% 2 == 1) %>% unlist()

# Shift the longitude of every second latitude to the right to make hex structure
grid <- grid %>%
    dplyr::mutate(hex_long = ifelse(hex_lat %in% shift_lat, hex_long,
        hex_long + (hex_size / 2))) %>%
    dplyr::mutate(id=1:NROW(.)) %>%
    dplyr::mutate(assigned=FALSE)
```

```{r plot_shift}
ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a") + theme_void() + coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
```

@@

```{r grid_id}
full_grid <- grid <- grid %>%
    mutate(hex_long_int = dense_rank(hex_long)-1,
        hex_lat_int = dense_rank(hex_lat)-1)
```

### Step 2: Rolling windows

Not all of the grid points will be used, especially if islands impact the overall space covered.
To filter the grid for appropriate points for allocation,
the `create_buffer` function is called from `create_grid`.
It finds the amount of columns and rows needed to best capture the set of centroids.

```{r}
nlong <- length(unique(grid$hex_long))
nlat <- length(unique(grid$hex_lat))

centroids <- centroids %>%
  mutate(long_int = round((longitude-min(grid$hex_long))/(max(grid$hex_long)-min(grid$hex_long))*nlong, 0),
          lat_int = round((latitude-min(grid$hex_lat))/(max(grid$hex_lat)-min(grid$hex_lat))*nlat, 0))
```

@@

```{r echo = FALSE}
# Amount of lats and longs in each group
lat_size = round(nlat/20,0)
long_size = round(nlong/20,0)
```

@@

```{r echo = FALSE}
 # make a list of groups, manual sliding windows
    nlat_list <- purrr::map2(seq(1:nlat), lat_size + seq(1:nlat), c)
    nlong_list <- purrr::map2(seq(1:nlong), long_size + seq(1:nlong), c)

    lat_window <- function(x, cents = centroids, maximum = nlat){
        max_int = min(x[2],maximum)

        cents_in <- filter(cents, between(lat_int, x[1], max_int))
        return(cents_in)
    }

    long_window <- function(x, cents = centroids, maximum = nlong){
        max_int = x[2]
        while (max_int > maximum){
            max_int = max_int - 1
        }

        cents_in <- filter(cents, between(long_int, x[1], max_int))
        return(cents_in)
    }

    # LATITUDE ROWS FILTER
    # amount of latitude in sliding window
    lat_windows <- purrr::map(.x = nlat_list, .f = lat_window)

    # find the min and max longitude for each latitude
    range_rows <- purrr::map_dfr(.x = lat_windows,
        .f = function(x) {x %>%
                dplyr::summarise(
                    long_min = ifelse(purrr::is_empty(long_int), NA, min(x$long_int)),
                    long_max = ifelse(purrr::is_empty(long_int), NA, max(x$long_int))
                )}
    )
```

@@

```{r echo = FALSE}
 # smooth the minimums
    av_range_rows <- purrr::map_dfr(.x = nlat_list, .f = function(x, rows = range_rows) {
        rows[x[1]:min(x[2], NROW(rows)),] %>%
            dplyr::summarise(mean_long_min = mean(long_min, na.rm=T), mean_long_max = mean(long_max, na.rm=T))
    }) %>%
        bind_cols(lat_id = c(seq(1:nlat) +lat_size), .)

    # LONGITUDE COLS FILTER
    long_windows <- purrr::map(.x = nlong_list, .f = long_window, centroids, nlong)

    # find the min and max longitude for each latitude
    range_cols <- purrr::map_dfr(.x = long_windows, .f = function(x) { x %>%
            dplyr::summarise(
                lat_min = ifelse(purrr::is_empty(lat_int), NA, min(x$lat_int)),
                lat_max = ifelse(purrr::is_empty(lat_int), NA, max(x$lat_int))
            )}
    )

    # smooth the minimums
    av_range_cols <- purrr::map_dfr(.x = nlong_list, .f = function(x, cols = range_cols) {
        cols[x[1]:min(x[2], NROW(cols)),] %>%
            dplyr::summarise(mean_lat_min = mean(lat_min, na.rm=T), mean_lat_max = mean(lat_max, na.rm=T))
    }) %>%
        bind_cols(long_id = c(seq(1:nlong) + round(long_size/2)), .)

```

<!--
Figure of rolling window construction
-->

### Step 3: Filtering the grid

@@

```{r echo = FALSE}
    # APPLY A BUFFER
    # change buffer to amount of hexagons (ints) either side
    hex_buffer <- floor(buffer_dist/hex_size)

    grid <- grid %>%
        left_join(., av_range_rows, by = c("hex_lat_int" = "lat_id")) %>%
        left_join(., av_range_cols, by = c("hex_long_int" = "long_id")) %>%
        rowwise() %>%
        mutate(long_buffer = ifelse(between(hex_long_int,mean_long_min - hex_buffer,
            mean_long_max + hex_buffer), "in", "out")) %>%
        mutate(lat_buffer = ifelse(between(hex_lat_int,mean_lat_min - hex_buffer,
            mean_lat_max + hex_buffer), "in", "out")) %>%
        filter(lat_buffer =="in" | long_buffer == "in")

```

```{r plot_buffer}
ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = full_grid, size = 0.25) +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75)
```

## Centroid to focal point distance

```{r split_centroids}
# Split the centroid data set
centroids <- centroids %>% 
  nest(longitude, latitude) %>% 
  mutate(closest = map(data, closest_focal_point, focal_points = capital_cities %>% filter(points == "Hobart"))) %>% 
  unnest(data, closest) %>% 
  arrange(focal_distance)
```

@@

## Allocation of centroids

The distance around a centroid to consider for possible hexagon locations is determined by the hex_filter. It multiplies the amount given by hex_filter, by the size of the hexagons to find the distance.

```{r}
## Consider hexagon points up to a certain distance from centroid
hex_filter <- 10
```

```{r}
width = 15
```

```{r, eval = FALSE}
hexmap_allocation <- allocate(centroids = centroids,
        hex_grid = grid,
        hex_size = hex_size,
        hex_filter = hex_filter,
        width = width,
        focal_points = capital_cities,
        verbose = TRUE,
        id = sf_id)
```

@@

```{r arrange}
s_centroids <- centroids %>% arrange(focal_distance)

s_centroids <- split(s_centroids, s_centroids[["focal_distance"]])

# Set up allocation data frame
centroid_allocation <- NULL
```

@@

```{r orig_dist}
# keep value to reset expanded distances
expand_dist <- hex_filter
```

@@

### Step 1: Filter the grid for unassigned hexagon points

@@

```{r available_points}
# filter for only the available hex grid points
hex_grid <- grid %>% filter(!assigned)
```

### Step 2: Filter the grid points for those closest to the centroid

@@

```{r close_points}
# filter grid for avaiable points
centroid1 <- centroids %>% head(1)

flong <- centroid1$longitude
flat <- centroid1$latitude

hex_grid <- hex_grid %>% ungroup() %>%
        filter(flat - buffer_dist < hex_lat & hex_lat < flat + buffer_dist) %>%
        filter(flong - buffer_dist < hex_long & hex_long < flong + buffer_dist)

```

@@

```{r, echo = FALSE}
ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75)

```

@@

```{r}
    hex_grid <- hex_grid %>%
        rowwise %>%
        mutate(
        hex_lat_c = hex_lat - flat,
        hex_long_c = hex_long - flong) %>%
        mutate(hyp = ((hex_lat_c^2) + (hex_long_c^2))^(1/2))

        f_angle <- centroid1 %>%
            mutate(atan = atan2(latitude-latitude1,longitude-longitude1),
                angle = (atan*180/pi),
                pangle = ifelse(angle<0, angle +360, angle)) %>% pull()

        hex_grid <- hex_grid %>%
            # create circle of radius: hex_filter
            filter(hyp < hex_filter) %>%
            mutate(
                # geosphere takes a long time
                angle = f_angle,
                angle_plus = (angle + width)%%360,
                angle_minus = (angle - width)%%360,
                atan = atan2(hex_lat_c, hex_long_c),
                hex_angle = (atan*180/pi),
                hex_angle = ifelse(hex_angle<0, hex_angle +360, hex_angle))

```

```{r, echo = FALSE}
ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75)
```

@@

```{r}
# Filter for angle within circle

        if (hex_grid$angle_minus[1] < hex_grid$angle_plus[1]) {
            hex_grid <- hex_grid %>%
                # create slice of 60 degrees from centroid
                filter(angle_minus < hex_angle & hex_angle < angle_plus)
        } else {
            hex_grid <- hex_grid %>%
                # create slice of 60 degrees from centroid
                filter(hex_angle < angle_plus | angle_minus > hex_angle)
        }

```

```{r}

ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75)

```

```{r}

# Choose first available point
        cent <- centroid1 %>% dplyr::rename(focal_point = points, focal_dist = focal_distance, focal_angle = angle)

        # Filter should give one hex point
        hex <- hex_grid %>% 
          ungroup %>% 
          filter(hyp == min(hyp)) %>%
          select(hex_long, hex_lat, hex_id = id)

        #update grid to show this centroid as assigned
        hex_grid[which(hex_grid$id == hex$hex_id),]$assigned <- TRUE

        centroid_allocation <- bind_rows(centroid_allocation, dplyr::bind_cols(cent, hex)) %>% as_tibble()

```

@@

```{r}
hex_points_df <- centroid_allocation %>% 
  fortify_hexagon(hex_size = hex_size)
```

```{r}
ggplot(hex_points_df) + 
  geom_polygon(aes(x = long, y = lat, group = LGA_CODE16)) +
  coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75)
```

```{r fullhexmap}
# Create centroids set
centroids <- create_centroids(tas_lga, "LGA_CODE16")
# Create hexagon location grid
grid <- create_grid(centroids = centroids, hex_size = 0.25, buffer_dist = 1.2)
# Allocate polygon centroids to hexagon grid points
hex_allocated <- allocate(centroids = centroids,
hex_grid = grid,
sf_id = "LGA_CODE16",
hex_size = 0.25, # same size used in create_grid
hex_filter = 10,
focal_points = capital_cities,
width = 30, verbose = FALSE) # same column used in create_centroids
```

```{r}
h1 <- hex_allocated %>%
  fortify_hexagon(hex_size = 0.25) %>% 
  left_join(., tas_lga)

p1 <- fortify_sfc(tas_lga)

end_hex <- ggplot() +
  geom_polygon(data = p1, aes(x=long, lat, group = group), alpha = 0.1) +
  geom_polygon(data = h1, aes(x=long, lat, group = LGA_CODE16)) + theme_void() + coord_equal()

gridExtra::grid.arrange(end_hex, end_cents)
```

## Applications of algorithm

<!--
Is  your  solution  always  working?  
Can  you  prove it? 
How does it work? 
-->

@@

<!--
Is your analysis about worst case or average case? 
What kind of theoretical and analytical support can you give for your proposed scheme/solution? 
-->

@@

>>>>

% !TeX root = RJwrapper.tex
\title{An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With
Application to Australian Maps}
\author{by Stephanie Kobakian, Dianne Cook}

\maketitle

\abstract{%
This algorithm creates a hexagon to represent each of the spatial
polygons provided. It allocates these hexagon in a manner that preserves
the spatial relationship of the areas. It showcases spatial
distributions, by emphasising the small geograhical regions that are
often diffcult to locate on large geographic maps.
}

% Any extra LaTeX you need in the preamble

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

@@

\hypertarget{motivation}{%
\subsection{Motivation}\label{motivation}}

@@

\hypertarget{algorithm}{%
\section{Algorithm}\label{algorithm}}

Our solution operates on a set of polygons. There are parameters used in
the process that may be provided, or will be automatically derived. All
necessary functions are exported, with a main function
\texttt{create\_hexmap} used to step through these automatically.

\hypertarget{parameters}{%
\subsection{Parameters}\label{parameters}}

The \texttt{create\_hexmap} function requires several parameters, if
they are not provided, the information will be derived from the polygon
set used.

\textbf{The following must be provided to \texttt{create\_hexmap}:}

\begin{Schunk}

\begin{tabular}{l|l}
\hline
parameter & description\\
\hline
shp & an Rdata object containing the polygon information\\
\hline
shp\_path & character string location of the shape file that contains the polygon information\\
\hline
sf\_id & name of a unique column that distinguishes areas\\
\hline
capital\_cities & a data frame of reference locations used to allocate hexagons\\
\hline
\end{tabular}

\end{Schunk}

The polygon set of Local Government Areas in Tasmania in 2016 is stored
in the sugarbag package data as \texttt{tas\_lga}. A single column of
the data set must be used as a unique identifier of areas. In this case,
the unique LGA codes associated with each LGA have been used, their
names could have also been used.

@@

\textbf{The following parameters will be determined within
\texttt{create\_hexmap} if not provided. They are created throughout the
following example:}

\begin{Schunk}

\begin{tabular}{l|l}
\hline
parameter & description\\
\hline
buffer\_dist & a float value for distance in degrees to extend beyond the - geometry provided\\
\hline
hex\_size & a float value in degrees for the diameter of the hexagons\\
\hline
hex\_filter & amount of hexagons around centroid to consider for allocation\\
\hline
width & the angle used to filter the grid points around a centroid\\
\hline
\end{tabular}

\end{Schunk}

When utilising individual \texttt{sugarbag} functions, we recommend the
following approach:

\hypertarget{polygon-information}{%
\subsection{Polygon Information}\label{polygon-information}}

Begin with a set of polygons. The set should be provided as an
\texttt{sf} object, this is a data frame containing a \texttt{geometry}
column. The \texttt{read\_shape} function can assist in creating this
object. We will use the Loca Goverment Areas of Tasmania, sourced from
the Australian Bureau of Statistics.

\begin{Schunk}
\begin{figure}
\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-3-1} \caption[lga Local Government Areas and derived centroids]{lga Local Government Areas and derived centroids.}\label{fig:unnamed-chunk-3}
\end{figure}
\end{Schunk}

\hypertarget{hexagon-grid}{%
\subsection{Hexagon grid}\label{hexagon-grid}}

Each new hexagon will need to tesselate, a grid is created to ensure a
close point is found, that will allow all areas to tesselate, this is
inspired by tilegrams. The grid of possible hexagon centroids can be
made using the \texttt{create\_grid} function. The grid creation takes
several steps. It requires the centroids, the hexagon size and the
buffer distance.

\hypertarget{step-1-expand-the-grid}{%
\subsubsection{Step 1: Expand the grid}\label{step-1-expand-the-grid}}

@@

\begin{Schunk}

\includegraphics{algorithmRjournal_files/figure-latex/plot_grid-1} \end{Schunk}

@@

\begin{Schunk}

\includegraphics{algorithmRjournal_files/figure-latex/plot_shift-1} \end{Schunk}

@@

\hypertarget{step-2-rolling-windows}{%
\subsubsection{Step 2: Rolling windows}\label{step-2-rolling-windows}}

Not all of the grid points will be used, especially if islands impact
the overall space covered. To filter the grid for appropriate points for
allocation, the \texttt{create\_buffer} function is called from
\texttt{create\_grid}. It finds the amount of columns and rows needed to
best capture the set of centroids.

@@

@@

@@

\hypertarget{step-3-filtering-the-grid}{%
\subsubsection{Step 3: Filtering the
grid}\label{step-3-filtering-the-grid}}

@@

\begin{Schunk}

\includegraphics{algorithmRjournal_files/figure-latex/plot_buffer-1} \end{Schunk}

\hypertarget{centroid-to-focal-point-distance}{%
\subsection{Centroid to focal point
distance}\label{centroid-to-focal-point-distance}}

@@

\hypertarget{allocation-of-centroids}{%
\subsection{Allocation of centroids}\label{allocation-of-centroids}}

The distance around a centroid to consider for possible hexagon
locations is determined by the hex\_filter. It multiplies the amount
given by hex\_filter, by the size of the hexagons to find the distance.

@@

@@

@@

\hypertarget{step-1-filter-the-grid-for-unassigned-hexagon-points}{%
\subsubsection{Step 1: Filter the grid for unassigned hexagon
points}\label{step-1-filter-the-grid-for-unassigned-hexagon-points}}

@@

\hypertarget{step-2-filter-the-grid-points-for-those-closest-to-the-centroid}{%
\subsubsection{Step 2: Filter the grid points for those closest to the
centroid}\label{step-2-filter-the-grid-points-for-those-closest-to-the-centroid}}

@@

@@

\begin{Schunk}

\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-12-1} \end{Schunk}

@@

\begin{Schunk}

\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-14-1} \end{Schunk}

@@

\begin{Schunk}

\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-16-1} \end{Schunk}

@@

\begin{Schunk}

\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-19-1} \end{Schunk}

\begin{Schunk}

\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-20-1} \end{Schunk}

\hypertarget{applications-of-algorithm}{%
\subsection{Applications of algorithm}\label{applications-of-algorithm}}

@@

@@

\address{%
Stephanie Kobakian\\
Queensland Univeristy of Technology\\
\\
}
\href{mailto:stephanie.kobakian@monash.edu}{\nolinkurl{stephanie.kobakian@monash.edu}}

\address{%
Dianne Cook\\
Monash University\\
\\
}
\href{mailto:dicook@monash.edu}{\nolinkurl{dicook@monash.edu}}
